### 2020-04-09 Thesis-Chapter1-Introduction.tex
Move EA alternatives to own section

\eestart

\ee{The discussion must go on} As long as regulators continue pursuing \ac{EA} regulation, it is the responsibility of
the technical community to engage and respect the valid arguments being presented.

\ee{Cryptography is foundational} Strong cryptography in its various forms is foundational to digital security.

\ee{Investigators need data} The ability to access digital data for investigation and prosecution is important today and
will be increasingly important in the future.

\ee{Mass surveillance is a danger} Mass surveillance, which \ac{EA} makes easier, is a grave danger from which
representative governments are not immune.

\ee{Transparency is necessary} Transparency of the law enforcement and intelligence communities' data access capability
and usage is critical for public trust.

\ee{\Ac{EA} is an international problem} The internet is largely borderless, and international and human rights
considerations significantly constrain workable \ac{EA} solutions.

\ee{Perfection is not the goal} To loosely quote the ``insecurity axioms,'' insecurity cannot be destroyed, only moved
around \cite{nrc_schneider_1999}. \Ac{EA}, like all security, is a matter of finding the right balance of risk.

\eeend

>>>>

\newcommand{\principlesstart}{\begin{enumerate}}
\newcommand{\principle}[1]{\item \textbf{#1.}}
\newcommand{\principlesend}{\end{enumerate}}

\principlesstart

\principle{The discussion must go on} As long as regulators continue pursuing \ac{EA} regulation, it is the
responsibility of the technical community to engage and respect the valid arguments being presented.

\principle{Cryptography is foundational} Strong cryptography in its various forms is foundational to digital security.

\principle{Investigators need data} The ability to access digital data for investigation and prosecution is important
today and will be increasingly important in the future.

\principle{Mass surveillance is a danger} Mass surveillance, which \ac{EA} makes easier, is a grave danger from which
representative governments are not immune.

\principle{Transparency is necessary} Transparency of the law enforcement and intelligence communities' data access
capability and usage is critical for public trust.

\principle{\Ac{EA} is an international problem} The internet is largely borderless, and international and human rights
considerations significantly constrain workable \ac{EA} solutions.

\principle{Perfection is not the goal} To loosely quote the ``insecurity axioms,'' insecurity cannot be destroyed, only
moved around \cite{nrc_schneider_1999}. \Ac{EA}, like all security, is a matter of finding the right balance of risk.

\principlesend
